### 2024-06-06 conteudo/01-exemplo-normas-ime.tex
More work of 05/06/2024

\subsection{Types of code duplication}

The categorization of two code artifacts as a duplication of each other is a subjective task (REFERENCE HERE). 
To mitigate this human aspect on the given problem, the literature classified code duplication on the scale of changes between 
the code artifacts in four main types of code dlone duplication \citep{litreview}. Given two code artifacts F and G, 
the types of Code Duplication are described as follow \citep{litreview}:

@@

>>>>

\subsection{Types of code clone duplication}

The categorization of two code artifacts as a duplication of each other is a subjective task (REFERENCE HERE). 
To mitigate this human aspect on the given problem, the literature classified code duplication on the scale of changes between 
the code artifacts in four main types of code clone duplication \citep{litreview}. Given two code artifacts F and G, 
the types of Code Duplication are described as follow \citep{litreview}:

@@

Given the complexity of Types 3 and 4 of code duplications, the state-of-art approches that aims at this type of
duplication constantly have a high cost in computational time and memory space \citep{letreview}, which is a concern in our research 
that aim to work in large codebases scopes. For this reason we will look after mainly at Type 1 and 2 of code duplications.
